QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-09-13 paper.tex
Rev_RelatedWorkTable_V0.5

		\lettrine{M}{ \,OBILE} edge computing (MEC) \cite{mao2017survey} has emerged as a promising technological solution to overcome the challenges faced by mobile devices (MDs) when performing high computational tasks, such as real-time data processing and artificial intelligence applications \cite{zhou2019edge} \cite{yousefpour2019all}. In spite of the MDs' technological advancements, their limited computing power and \textcolor{blue}{energy} may lead to task drops, processing delays, and an overall poor user experience. By offloading intensive tasks to nearby edge nodes (ENs), MEC effectively empowers computation capability and reduces the delay and energy consumption. This improvement enhances the users' QoE, especially for time-sensitive computation tasks \cite{TNSE-QOE-24} \cite{ shah2018hierarchical}.

@@

		%methods, advances, drawbacks \textcolor{blue}
		\begin{table*}[htbp]\textcolor{blue}{

@@

		In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, \textcolor{blue}{energy status}, and historical workloads at the ENs. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

			\item \textit{DRL-based Offloading Algorithm:} To address the problem of long-term QoE maximization, we focus on task completion, task delay, and energy consumption to quantify the MDs' QoE. We propose QECO algorithm based on DRL that empowers each MD to make offloading decisions independently, without prior knowledge of the other MDs' tasks and offloading models. With a focus on the MD's \textcolor{blue}{energy level}, our approach leverages deep Q-network (DQN) \cite{mnih2015human} and long short-term memory (LSTM) \cite{hochreiter1997long} to prioritize and strike an appropriate balance between QoE factors. We also analyze the training convergence and complexity of the proposed algorithm.

@@

		Based on the introduced system model, we present the computation task offloading problem in this section. Our primary goal is to enhance each MD's QoE individually by taking the dynamic demands of MDs into account. To achieve this, we approach the optimization problem as an MDP, aiming to maximize the MD's QoE by striking a balance among key QoE factors, including task completion, task delay, and energy consumption. To prioritize QoE factors, we utilize the MD's \textcolor{blue}{energy level}, which plays a crucial role in decision-making. Specifically, when an MD observes its state (e.g. task size, queue details, and \textcolor{blue}{energy status}) and encounters a newly arrived task, it selects an appropriate action for that task. The selected action, based on the observed state, will result in enhanced QoE. Each MD strives to maximize its long-term QoE by optimizing the policy mapping from states to actions. In what follows, we first present the state space, action space, and QoE function, respectively. We then formulate the QoE maximization problem for each MD.

		\subsection{State Space}
		A state in our MDP represents a conceptual space that comprehensively describes the state of an MD facing the environment. We represent the MD $i$'s state in time slot $t$ as vector $\boldsymbol{s}_i(t)$ that includes the newly arrived task size, the queues information, the MD's \textcolor{blue}{energy level}, and the workload history at the ENs. The MD observers this vector at the beginning of each time slot. The vector $\boldsymbol{s}_i(t)$ is defined as follows:
		\begin{alignat}{1}
			\boldsymbol{s}_i(t) = \Big(\lambda_i(t), \delta_i^{\text{C}}(t), \delta_i^{\text{T}}(t), \boldsymbol{\eta}_i^{\text{E}}\hspace{-0.4mm}(\hspace{-0.4mm}t\hspace{-0.4mm}-\hspace{-0.4mm}1\hspace{-0.5mm}),\phi_i(t), \mathcal{H}(t) \Big),
			\label{18}
		\end{alignat}
		where vector $\boldsymbol{\eta}_i^{\text{E}}(t-1) = (\eta_{i,j}^{\text{E}}(t-1))_{j \in \mathcal{J}}$ represents the queues length of MD $i$ in ENs at the previous time slot and is computed by the MD according to \eqref{10}. Let $\phi_i(t)$ denote the \textcolor{blue}{energy level} of MD $i$ in time slot $t$. Considering the power modes of \textcolor{blue}{some} real mobile device, $\phi_i(t)$ is derived from the discrete set $\Phi=\{\phi_1,\phi_2,\phi_3\}$, corresponding to ultra power-saving, power-saving, and performance modes, respectively.

@@

		$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
		\begin{alignat}{1}
			\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
			\label{23}  
		\end{alignat}
		where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. When the MD is operating in performance mode, the primary focus is on minimizing task delays, thus the delay contributes more to the cost. On the other hand, when the MD switches to ultra power-saving mode, the main attention is directed toward reducing power consumption.

@@

		\begin{algorithm} [tbp]
			\caption{QECO Algorithm (Offloading Decision)}\label{alg:cap}
			\begin{algorithmic}[1]
				\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
				\renewcommand{\algorithmicensure}{\textbf{Output:}}
				\Require state space $\mathcal{S}$, action space $\mathcal{A}$
				\Ensure MD $i \in \mathcal{I}$ experience  \textcolor{blue}{ $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$}
				\For {episode 1 to $N^{\text{ep}}$}
				\State Initialize $\boldsymbol{s}_i(1)$
				\For {time slot $t \in \mathcal{T}$}
				\If{MD $i$ receives a new task $z_i(t)$}
				\State Send an \textit{UpdateRequest} to EN $j_i$;
				\State Receive network parameter vector $\theta_i^{\text{E}}$;
				\State Select action $\boldsymbol{a}_i(t)$ based on \eqref{26};
				\EndIf
				\State Observe a set of QoEs $\{\boldsymbol{q}_i(t'), t' \in \mathcal{F}_i^t\}$;
				\State Observe\textcolor{white}{i}the next\textcolor{white}{i}state $\textbf{\textit{s}}_i(t+1)$;\textcolor{white}{i}
				\For {each task $z_i(t')$ where $t' \in \mathcal{F}_i^t$} 
				\State Send \hspace{-1mm} $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ to EN $j_i$;
				\EndFor
				\EndFor
				\EndFor
			\end{algorithmic}
		\end{algorithm}

@@

		\begin{algorithm}[tbp]
			\caption{QECO Algorithm (Training Process)}\label{alg:cap2}
			\begin{algorithmic}[1]
				\renewcommand{\algorithmicrequire}{\textbf{\textcolor{blue}{Input:}}} 
				\renewcommand{\algorithmicensure}{\textbf{\textcolor{blue}{Output:}}}
				\Require \textcolor{blue}{experience $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$ from MD $i \in \mathcal{I}$}
				\Ensure \textcolor{blue}{The parameters vector $\theta_i^{\text{E}}$ }
				\State Initialize replay buffer $\mathcal{M}_i$ for each MD $i \in \mathcal{I}_j$;
				\State Initialize $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ with random parameters $\theta_i^{\text{E}}$ and $\theta_i^{\text{T}}$ respectively, for each MD $i \in \mathcal{I}_j$;
				\State Set Count := 0
				\While{True} \Comment{\textit{infinite loop}}
				\If{receive an \textit{UpdateRequest} from MD $i \in \mathcal{I}_j$}
				\State Send $\theta_i^{\text{E}}$ to MD $i \in \mathcal{I}$;
				\EndIf
				\If {an experience \hspace{-0.2mm} $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$ is received \\ \;\;\;\; from MD $i \in \mathcal{I}_j$}
				\State Store $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ in $\mathcal{M}_i$;
				\State Get a collection of experiences  $\mathcal{I}$ from $\mathcal{M}_i$; 
				\For{each experience $i \in \mathcal{I}$} 
				\State Get experience $(\boldsymbol{s}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}n\hspace{-0.5mm}+1\hspace{-0.2mm}))$; 
				\State Generate $\hat{Q}_{i,n}^{\text{T}}$ according to   \eqref{28};
				\EndFor
				\State Set vector  $\hat{\mathbf{Q}}_i^{\text{T}} := (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$;
				\State Update $\theta_i^{\text{E}}$ to minimize $L(\theta_i^{\text{E}}$, $\hat{\mathbf{Q}}_i^{\text{T}})$ in   \eqref{30};
				\State Count := Count + 1;
				\If {mod(Count, \textit{ReplaceThreshold}) = 0}
				\State $\theta_i^{\text{T}}$ := $\theta_i^{\text{E}}$;
				\EndIf
				\EndIf
				\EndWhile

@@

		The EN randomly selects a sample collection of experiences from the replay buffer, denoted as $\mathcal{N}$. For each experience $n \in \mathcal{N}$, it calculates the value of $	\hat{Q}^{\text{T}}_{i,n}$. This value represents the QoE in experience $n$ and includes a discounted Q-value of the action anticipated to be taken in the subsequent state of experience $n$, according to the network $\textit{Net}^\text{T}_i$, given by
		\begin{alignat}{1}
			\hat{Q}_{i,n}^{\text{T}} = \boldsymbol{q}_i(n) + \gamma Q_i^{\text{T}}(\boldsymbol{s}_i(n+1)), \tilde{\boldsymbol{a}}_n; \theta_i^{\text{T}}),
			\label{28}  
		\end{alignat}  
		where $\tilde{\boldsymbol{a}}_n$ denotes the optimal action for the state $\boldsymbol{s}_i(n+1)$ based on its highest Q-value under $\textit{Net}_i^{\text{E}}$, as given by:
		\begin{alignat}{1}
			\tilde{\boldsymbol{a}}_n = \text{arg} \; \max_{\boldsymbol{a} \in \mathcal{A}} \; Q_i^{\text{E}}(\boldsymbol{s}_i(n+1), \boldsymbol{a}; \theta_i^{\text{E}}).
			\label{29}  
		\end{alignat} 
		In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. %based on $\textit{Net}_i^{\text{T}}_i$, i.e., $\gamma Q_i^{\text{T}}(\mathcal{S}_i(i+1)), \mathcal{A}_i^{\text{N}}; \theta_i^{\text{T}})$
		%Based on the set $\mathcal{N}$, the EN trains the MD's neural network using previous sample experiences. Simultaneously, it updates $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ and computes vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
		\textcolor{blue}{Based on the previous sample experiences $\mathcal{N}$, the EN computes the vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$ and trains the MD's neural network (in steps 11-21 of Algorithm ~\ref{alg:cap2}) to keep parameter vector $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ update for the MD's \textit{UpdateRequest}}. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:

@@

		\subsection{Simulation Setup}
		We consider a MEC environment with 50 MDs and 5 ENs, similar to \cite{9253665}. We also follow the model presented in \cite{zhou2021deep} to determine the energy consumption. All the parameters are given in Table~\ref{table}. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, each of length 0.1 second. The QECO algorithm incorporates real-time experience into its training process to continuously enhance the offloading strategy. Specifically, we employ a batch size of 16, maintain a fixed learning rate of 0.001, and set the discount factor $\gamma$ to 0.9. The probability of random exploration gradually decreases from an initial value 1, progressively approaching 0.01, all of which is facilitated by an RMSProp optimizer. \textcolor{blue}{Detailed settings regarding the neural networks and simulation can be found at our github repository.\footnote{\textcolor{blue}{The code for reproducing the simulation results of this letter is available at: \href{https://github.com/ImanRHT/QECO}{https://github.com/ImanRHT/QECO.}}}}

@@

		\begin{table}
			\renewcommand{\arraystretch}{1.2}
			\captionsetup{name=TABLE}
			\caption{Simulation Parameters}
			\scalebox{1.05}{%
				\begin{tabular}{ l|l } 
					\toprule
					\textbf{Parameter} & \textbf{Value}  \\ 
					\midrule
					%Number of MDs $i$  & 50  \\ 
					%Number of EN $j$  & 5  \\ 
					%Number of episodes $N^{\text{ep}}$  & 1000  \\ 
					%Number of time slots $T$  & 100 (with $\tau = 0.1$ second) \\ 
					Computation capacity of MD $f_i$  & 2.6 GHz \\ 
					Computation capacity of EN $f_j^{\text{E}}$ & 42.8 GHz  \\ 
					Transmission capacity of MD $r_{i,j}(t)$ & 14 Mbps  \\ 
					Task arrival rate & 150 Task/sec  \\ 
					Size of task $\lambda_i(t)$  & $\{\text{1.0, 1.1, \ldots , 7.0}\}$ Mbits \\ 
					Required CPU cycles of task $\rho_i(t)$  & $\{\text{0.197,0.297,0.397}\}$ $\times10^3$ \\ 
					Deadline of task $ \Delta_i$  & 10 time slots (1 Sec)\\ 
					\textcolor{blue}{Energy level} percentage of MD $\phi_i(t)$  & $\{\text{25, 50, 75}\}$\\ %Percent \\ 
					%Computation power of MD $p_i^{\text{C}}$ & \text{$10^{-27}(f_i)^3$}  \\ 
					Computation power of EN $p_j^{\text{E}}$ & 5 W  \\ 
					Transmission power of MD $p_i^{\text{T}}$ & 2.3 W  \\ 
					Standby power of MD $p_i^{\text{I}}$& 0.1 W  \vspace{1mm}\\ 
					\toprule
			\end{tabular}}
			\label{table}
		\end{table}

>>>>

		\lettrine{M}{ \,OBILE} edge computing (MEC) \cite{mao2017survey} has emerged as a promising technological solution to overcome the challenges faced by mobile devices (MDs) when performing high computational tasks, such as real-time data processing and artificial intelligence applications \cite{zhou2019edge} \cite{yousefpour2019all}. In spite of the MDs' technological advancements, their limited computing power and \textcolor{black}{energy} may lead to task drops, processing delays, and an overall poor user experience. By offloading intensive tasks to nearby edge nodes (ENs), MEC effectively empowers computation capability and reduces the delay and energy consumption. This improvement enhances the users' QoE, especially for time-sensitive computation tasks \cite{TNSE-QOE-24} \cite{ shah2018hierarchical}.

@@

		%methods, advances, drawbacks \textcolor{black}
		\begin{table*}[htbp]\textcolor{black}{

@@

		In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, \textcolor{black}{energy status}, and historical workloads at the ENs. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

			\item \textit{DRL-based Offloading Algorithm:} To address the problem of long-term QoE maximization, we focus on task completion, task delay, and energy consumption to quantify the MDs' QoE. We propose QECO algorithm based on DRL that empowers each MD to make offloading decisions independently, without prior knowledge of the other MDs' tasks and offloading models. With a focus on the MD's \textcolor{black}{energy level}, our approach leverages deep Q-network (DQN) \cite{mnih2015human} and long short-term memory (LSTM) \cite{hochreiter1997long} to prioritize and strike an appropriate balance between QoE factors. We also analyze the training convergence and complexity of the proposed algorithm.

@@

		Based on the introduced system model, we present the computation task offloading problem in this section. Our primary goal is to enhance each MD's QoE individually by taking the dynamic demands of MDs into account. To achieve this, we approach the optimization problem as an MDP, aiming to maximize the MD's QoE by striking a balance among key QoE factors, including task completion, task delay, and energy consumption. To prioritize QoE factors, we utilize the MD's \textcolor{black}{energy level}, which plays a crucial role in decision-making. Specifically, when an MD observes its state (e.g. task size, queue details, and \textcolor{black}{energy status}) and encounters a newly arrived task, it selects an appropriate action for that task. The selected action, based on the observed state, will result in enhanced QoE. Each MD strives to maximize its long-term QoE by optimizing the policy mapping from states to actions. In what follows, we first present the state space, action space, and QoE function, respectively. We then formulate the QoE maximization problem for each MD.

		\subsection{State Space}
		A state in our MDP represents a conceptual space that comprehensively describes the state of an MD facing the environment. We represent the MD $i$'s state in time slot $t$ as vector $\boldsymbol{s}_i(t)$ that includes the newly arrived task size, the queues information, the MD's \textcolor{black}{energy level}, and the workload history at the ENs. The MD observers this vector at the beginning of each time slot. The vector $\boldsymbol{s}_i(t)$ is defined as follows:
		\begin{alignat}{1}
			\boldsymbol{s}_i(t) = \Big(\lambda_i(t), \delta_i^{\text{C}}(t), \delta_i^{\text{T}}(t), \boldsymbol{\eta}_i^{\text{E}}\hspace{-0.4mm}(\hspace{-0.4mm}t\hspace{-0.4mm}-\hspace{-0.4mm}1\hspace{-0.5mm}),\phi_i(t), \mathcal{H}(t) \Big),
			\label{18}
		\end{alignat}
		where vector $\boldsymbol{\eta}_i^{\text{E}}(t-1) = (\eta_{i,j}^{\text{E}}(t-1))_{j \in \mathcal{J}}$ represents the queues length of MD $i$ in ENs at the previous time slot and is computed by the MD according to \eqref{10}. Let $\phi_i(t)$ denote the \textcolor{black}{energy level} of MD $i$ in time slot $t$. Considering the power modes of \textcolor{black}{some} real mobile device, $\phi_i(t)$ is derived from the discrete set $\Phi=\{\phi_1,\phi_2,\phi_3\}$, corresponding to ultra power-saving, power-saving, and performance modes, respectively.

@@

		$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
		\begin{alignat}{1}
			\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
			\label{23}  
		\end{alignat}
		where $\phi_i(t)$ represents the MD $i$'s \textcolor{black}{energy level}. When the MD is operating in performance mode, the primary focus is on minimizing task delays, thus the delay contributes more to the cost. On the other hand, when the MD switches to ultra power-saving mode, the main attention is directed toward reducing power consumption.

@@

		\begin{algorithm} [tbp]
			\caption{QECO Algorithm (Offloading Decision)}\label{alg:cap}
			\begin{algorithmic}[1]
				\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
				\renewcommand{\algorithmicensure}{\textbf{Output:}}
				\Require state space $\mathcal{S}$, action space $\mathcal{A}$
				\Ensure MD $i \in \mathcal{I}$ experience  \textcolor{black}{ $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$}
				\For {episode 1 to $N^{\text{ep}}$}
				\State Initialize $\boldsymbol{s}_i(1)$
				\For {time slot $t \in \mathcal{T}$}
				\If{MD $i$ receives a new task $z_i(t)$}
				\State Send an \textit{UpdateRequest} to EN $j_i$;
				\State Receive network parameter vector $\theta_i^{\text{E}}$;
				\State Select action $\boldsymbol{a}_i(t)$ based on \eqref{26};
				\EndIf
				\State Observe a set of QoEs $\{\boldsymbol{q}_i(t'), t' \in \mathcal{F}_i^t\}$;
				\State Observe\textcolor{white}{i}the next\textcolor{white}{i}state $\textbf{\textit{s}}_i(t+1)$;\textcolor{white}{i}
				\For {each task $z_i(t')$ where $t' \in \mathcal{F}_i^t$} 
				\State Send \hspace{-1mm} $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ to EN $j_i$;
				\EndFor
				\EndFor
				\EndFor
			\end{algorithmic}
		\end{algorithm}

@@

		\begin{algorithm}[tbp]
			\caption{QECO Algorithm (Training Process)}\label{alg:cap2}
			\begin{algorithmic}[1]
				\renewcommand{\algorithmicrequire}{\textbf{\textcolor{black}{Input:}}} 
				\renewcommand{\algorithmicensure}{\textbf{\textcolor{black}{Output:}}}
				\Require \textcolor{black}{experience $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$ from MD $i \in \mathcal{I}$}
				\Ensure \textcolor{black}{The parameters vector $\theta_i^{\text{E}}$ }
				\State Initialize replay buffer $\mathcal{M}_i$ for each MD $i \in \mathcal{I}_j$;
				\State Initialize $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ with random parameters $\theta_i^{\text{E}}$ and $\theta_i^{\text{T}}$ respectively, for each MD $i \in \mathcal{I}_j$;
				\State Set Count := 0
				\While{True} \Comment{\textit{infinite loop}}
				\If{receive an \textit{UpdateRequest} from MD $i \in \mathcal{I}_j$}
				\State Send $\theta_i^{\text{E}}$ to MD $i \in \mathcal{I}$;
				\EndIf
				\If {an experience \hspace{-0.2mm} $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$ is received \\ \;\;\;\; from MD $i \in \mathcal{I}_j$}
				\State Store $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ in $\mathcal{M}_i$;
				\State Get a collection of experiences  $\mathcal{I}$ from $\mathcal{M}_i$; 
				\For{each experience $i \in \mathcal{I}$} 
				\State Get experience $(\boldsymbol{s}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}n\hspace{-0.5mm}+1\hspace{-0.2mm}))$; 
				\State Generate $\hat{Q}_{i,n}^{\text{T}}$ according to   \eqref{28};
				\EndFor
				\State Set vector  $\hat{\mathbf{Q}}_i^{\text{T}} := (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$;
				\State Update $\theta_i^{\text{E}}$ to minimize $L(\theta_i^{\text{E}}$, $\hat{\mathbf{Q}}_i^{\text{T}})$ in   \eqref{30};
				\State Count := Count + 1;
				\If {mod(Count, \textit{ReplaceThreshold}) = 0}
				\State $\theta_i^{\text{T}}$ := $\theta_i^{\text{E}}$;
				\EndIf
				\EndIf
				\EndWhile

@@

		The EN randomly selects a sample collection of experiences from the replay buffer, denoted as $\mathcal{N}$. For each experience $n \in \mathcal{N}$, it calculates the value of $	\hat{Q}^{\text{T}}_{i,n}$. This value represents the QoE in experience $n$ and includes a discounted Q-value of the action anticipated to be taken in the subsequent state of experience $n$, according to the network $\textit{Net}^\text{T}_i$, given by
		\begin{alignat}{1}
			\hat{Q}_{i,n}^{\text{T}} = \boldsymbol{q}_i(n) + \gamma Q_i^{\text{T}}(\boldsymbol{s}_i(n+1)), \tilde{\boldsymbol{a}}_n; \theta_i^{\text{T}}),
			\label{28}  
		\end{alignat}  
		where $\tilde{\boldsymbol{a}}_n$ denotes the optimal action for the state $\boldsymbol{s}_i(n+1)$ based on its highest Q-value under $\textit{Net}_i^{\text{E}}$, as given by:
		\begin{alignat}{1}
			\tilde{\boldsymbol{a}}_n = \text{arg} \; \max_{\boldsymbol{a} \in \mathcal{A}} \; Q_i^{\text{E}}(\boldsymbol{s}_i(n+1), \boldsymbol{a}; \theta_i^{\text{E}}).
			\label{29}  
		\end{alignat} 
		In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. %based on $\textit{Net}_i^{\text{T}}_i$, i.e., $\gamma Q_i^{\text{T}}(\mathcal{S}_i(i+1)), \mathcal{A}_i^{\text{N}}; \theta_i^{\text{T}})$
		%Based on the set $\mathcal{N}$, the EN trains the MD's neural network using previous sample experiences. Simultaneously, it updates $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ and computes vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
		\textcolor{black}{Based on the previous sample experiences $\mathcal{N}$, the EN computes the vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$ and trains the MD's neural network (in steps 11-21 of Algorithm ~\ref{alg:cap2}) to keep parameter vector $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ update for the MD's \textit{UpdateRequest}}. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:

@@

		\subsection{Simulation Setup}
		We consider a MEC environment with 50 MDs and 5 ENs, similar to \cite{9253665}. We also follow the model presented in \cite{zhou2021deep} to determine the energy consumption. All the parameters are given in Table~\ref{table}. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, each of length 0.1 second. The QECO algorithm incorporates real-time experience into its training process to continuously enhance the offloading strategy. Specifically, we employ a batch size of 16, maintain a fixed learning rate of 0.001, and set the discount factor $\gamma$ to 0.9. The probability of random exploration gradually decreases from an initial value 1, progressively approaching 0.01, all of which is facilitated by an RMSProp optimizer. \textcolor{black}{Detailed settings regarding the neural networks and simulation can be found at our github repository.\footnote{\textcolor{black}{The code for reproducing the simulation results of this letter is available at: \href{https://github.com/ImanRHT/QECO}{https://github.com/ImanRHT/QECO.}}}}

@@

		\begin{table}
			\renewcommand{\arraystretch}{1.2}
			\captionsetup{name=TABLE}
			\caption{Simulation Parameters}
			\scalebox{1.05}{%
				\begin{tabular}{ l|l } 
					\toprule
					\textbf{Parameter} & \textbf{Value}  \\ 
					\midrule
					%Number of MDs $i$  & 50  \\ 
					%Number of EN $j$  & 5  \\ 
					%Number of episodes $N^{\text{ep}}$  & 1000  \\ 
					%Number of time slots $T$  & 100 (with $\tau = 0.1$ second) \\ 
					Computation capacity of MD $f_i$  & 2.6 GHz \\ 
					Computation capacity of EN $f_j^{\text{E}}$ & 42.8 GHz  \\ 
					Transmission capacity of MD $r_{i,j}(t)$ & 14 Mbps  \\ 
					Task arrival rate & 150 Task/sec  \\ 
					Size of task $\lambda_i(t)$  & $\{\text{1.0, 1.1, \ldots , 7.0}\}$ Mbits \\ 
					Required CPU cycles of task $\rho_i(t)$  & $\{\text{0.197,0.297,0.397}\}$ $\times10^3$ \\ 
					Deadline of task $ \Delta_i$  & 10 time slots (1 Sec)\\ 
					\textcolor{black}{Energy level} percentage of MD $\phi_i(t)$  & $\{\text{25, 50, 75}\}$\\ %Percent \\ 
					%Computation power of MD $p_i^{\text{C}}$ & \text{$10^{-27}(f_i)^3$}  \\ 
					Computation power of EN $p_j^{\text{E}}$ & 5 W  \\ 
					Transmission power of MD $p_i^{\text{T}}$ & 2.3 W  \\ 
					Standby power of MD $p_i^{\text{I}}$& 0.1 W  \vspace{1mm}\\ 
					\toprule
			\end{tabular}}
			\label{table}
		\end{table}
